---
title: "Project"
author: "Ari Fleischer"
date: "11/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading in Libraries

```{r loading libraries, warning=FALSE, message=FALSE}
# Loading the libraries
library(tidyverse)
```

# Reading in US Counties 2015

```{r}
us_counties_2015 <- read_csv("acs2015_county_data.csv")
us_counties_2015
```

# Reading in US Counties 2015

```{r}
us_counties_2017 <- read_csv("acs2017_county_data.csv")
us_counties_2017
```

## Changing city in County Name to City

```{r}
us_counties_2017$County <- str_replace(us_counties_2017$County, "city", "City")
```

# Reading in Lat and Long Data

```{r}
lat_and_long <- read_csv("uscounties.csv")
lat_and_long
```

# Only Taking Columns We Want From Lat and Long

```{r}
lat_and_long1 <- lat_and_long[, c(6, 3, 7, 8)]
lat_and_long1
```

## Arraigning by State and then by County Name

```{r}
lat_and_long2 <- lat_and_long1 %>% arrange(state_name, county_full)
lat_and_long2
```

## Setting County Name in County 2015 to Be These County Name to Match

```{r}
us_counties_2015[1:3142, 3] <- lat_and_long2[2]
us_counties_2015[1:3142, 3]
```

# Rename Columns to Match US Counties

```{r}
colnames(lat_and_long1)[1:2] <- c("State", "County")
lat_and_long1
```

# Getting Complete Data For 3,142 US Counties and and County Equivalents 2015

```{r}
full_us_counties_2015_data <- us_counties_2015 %>% inner_join(lat_and_long1)
colnames(full_us_counties_2015_data)[38:39] <- c("Lat", "Long")
nrow(full_us_counties_2015_data)
full_us_counties_2015_data
```

# Getting Complete Data For 3,142 US Counties and and County Equivalents 2017

```{r}
full_us_counties_2017_data <- us_counties_2017 %>% inner_join(lat_and_long1)
colnames(full_us_counties_2017_data)[38:39] <- c("Lat", "Long")
nrow(full_us_counties_2017_data)
full_us_counties_2017_data 
```

# Writing Both Out to CSVs

```{r}
write_csv(full_us_counties_2015_data, "full_us_counties_2015_data.csv")
write_csv(full_us_counties_2017_data, "full_us_counties_2017_data.csv")
```

# Loading in Puerto Rico Lat and Long Data

```{r}
puerto_rico_lat_long <- read_csv("PuertoRicoLocationData.csv")
colnames(puerto_rico_lat_long)[1] <- "County"
puerto_rico_lat_long$`State` <- "Puerto Rico"

puerto_rico_lat_long1 <- puerto_rico_lat_long[, c(4,1,2,3)]
```

```{r}
puerto_rico_lat_long2 <- puerto_rico_lat_long1

puerto_rico_lat_long2$`County` <- paste0(puerto_rico_lat_long2$`County`,
                                         " Municipio")


puerto_rico_lat_long2$`County`
```

# Getting Complete Data For 78 Muncipalities in Puerto Rico 2015

```{r}
full_puerto_rico_2015_data <- us_counties_2015 %>% inner_join(puerto_rico_lat_long1)
nrow(full_puerto_rico_2015_data)
full_puerto_rico_2015_data
```

# Getting Complete Data For 78 Muncipalities in Puerto Rico 2017

```{r}
full_puerto_rico_2017_data <- us_counties_2017 %>% inner_join(puerto_rico_lat_long2)
nrow(full_puerto_rico_2017_data)
full_puerto_rico_2017_data
```

# Writing Puerto Rico Data Out to CSVs

```{r}
write_csv(full_puerto_rico_2015_data, "full_puerto_rico_2015_data.csv")
write_csv(full_puerto_rico_2017_data, "full_puerto_rico_2017_data.csv")
```

# Row Binding All of 2015 Together

```{r}
full_2015_county_data <- full_us_counties_2015_data %>% 
                         rbind(full_puerto_rico_2015_data)
nrow(full_2015_county_data)
```

# Row Binding All of 2017 Together

```{r}
full_2017_county_data <- full_us_counties_2017_data %>% 
                         rbind(full_puerto_rico_2017_data)
nrow(full_2017_county_data)
```

# Reading in Geographic Region for Each State

```{r}
geographic_region <- read_csv("us census bureau regions and divisions.csv")
geographic_region
```

# Add Region to Full Dataset

## 2015

```{r}
full_2015_county_data1 <- full_2015_county_data %>% inner_join(geographic_region)
full_2015_county_data2 <- full_2015_county_data1[, c(1, 3, 2, 40:42, 4:39)]
full_2015_county_data2
```

## 2017

```{r}
full_2017_county_data1 <- full_2017_county_data %>% inner_join(geographic_region)
full_2017_county_data2 <- full_2017_county_data1[, c(1, 3, 2, 40:42, 4:39)]
full_2017_county_data2
```


# Writing Full Data Out to CSVs

```{r}
write_csv(full_2015_county_data2, "full_2015_county_data.csv")
write_csv(full_2017_county_data2, "full_2017_county_data.csv")
```

# Getting Continetal US Data

## 2015

```{r}
continental_2015_county_data <- full_2015_county_data2 %>% 
  filter(!(`State Code` %in% c("AK", "HI", "PR")))
continental_2015_county_data
```

## 2017

```{r}
continental_2017_county_data <- full_2017_county_data2 %>% 
  filter(!(`State Code` %in% c("AK", "HI", "PR")))
continental_2017_county_data
```

## Writing Continental Data Out to CSVs

```{r}
write_csv(continental_2015_county_data, "continental_2015_county_data.csv")
write_csv(continental_2017_county_data, "continental_2017_county_data.csv")
```
